DOpElib: Differential Equations\\ and Optimization Environment

### 2013-01-08 Examples/description.tex
Adaptions in the nonstationary case for the dual-timesteppingscheme
Description um Opt Beispiel 9 erweitert
Docu of PDE/InstatPDE/Example1 has some flaws.
Update of the documentation, includes now higher order mappings.
deal.II -> Differential Equations and
TODO: Continue text for Exampe11

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib - Deal Optimization Environment}
\author{
  Christian Goll\thanks{Heidelberg University, 
    {christian.goll@iwr.uni-heidelberg.de}}, 
  Thomas Wick\thanks{Heidelberg University, 
    {thomas.wick@iwr.uni-heidelberg.de}}, 
  Winnifried Wollner\thanks{University of Hamburg, 
    {winnifried.wollner@math.uni-hamburg.de}}
}

@@

@@

\subsection{Nonstationary Stokes Equations}

@@

%\input{OPT/StatPDE/Example5/content.tex}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib: 
Differential Equations\\ and Optimization Environment}
\author{
  Christian Goll\thanks{Heidelberg University, 
    {christian.goll@iwr.uni-heidelberg.de}}, 
  Thomas Wick\thanks{Heidelberg University, 
    {thomas.wick@iwr.uni-heidelberg.de}}, 
  Winnifried Wollner\thanks{University of Hamburg, 
    {winnifried.wollner@math.uni-hamburg.de}}
}

@@

\subsection{Usage of Higher Order Mappings: Approximation of $\pi$}
\label{PDE_higher_order_mapping}
\input{PDE/StatPDE/Example10/content.tex}
\subsection{Stationary Stokes Equations with hp-Elements} 
\label{PDE_Stat_Stokes_hp}
\input{PDE/StatPDE/Example11/content.tex}

@@

\subsection{Nonstationary Navier-Stokes Equations}

@@

\input{OPT/StatPDE/Example9/content.tex}
\section{Subject to a Non-Stationary PDE}
\label{OPT_Instat}
\subsection{Control of a nonlinear heat equation via the initial values}
\label{OPT_Instat initial-value end-time}
\input{OPT/InstatPDE/Example1/content.tex}
